abxD01 Paper

### 2015-03-07 PAPER.Rmd
Change header
Add diversity to sfigure 2. Update code in paper.

> ### Differences between recovery days' thetayc
> 
> ### Statistical comparison of delayed and on time CFU results

>>>>

![**Supplemental Figure 2.**](supplemental/sfigure2ab.png)

**Supplemental Figure 2. Changes between untreated and recovery days.** A) The average thetaYC distance between pretreatment (day -11) and recovery days (days -5 through -1) is represented by circles connected by solid lines. Dashed lines with the same symbol indicate individual mice from the same cage. Antibiotic treatment is indicated by color. B) The average level of the inverse simpson diversity index is plotted by antibiotic treatment across time. Error bars show standard error of the mean. Mice were challenged with *C. difficile* on day 0.

> ### Supplemental Figure 2A: Differences between recovery days' thetayc

```{r, eval=FALSE}
file <- "~/Desktop/mothur/abxD01/abxD01.final.an.unique_list.0.03.recovery.vancomycin.thetayc.0.03.lt.ave.dist"
diffs <- getDistDiffs(file=file)

#metadata <- read.delim(file="~/Desktop/mothur/abxD01/searchme.txt", header = T, stringsAsFactors=F)
metadata$sample[1951] <- "007-1D1" # ID was messed up
names(metadata)[3] <- "group"

par(mfrow=c(2, 1))
par(mar=c(3, 5, 0.5, 0.5), las=2, mgp=c(3, 1, 0))
plot.dist.from(dist.from = diffs)

# Arrange diversity data for supplemental figure 2B

diversity <- read.delim(file="~/Desktop/mothur/abxD01/abxD01.final.an.unique_list.groups.ave-std.summary", sep="\t", header=T, stringsAsFactors=F)

diversity$group[2046] <- "007-1D1"
diversity$group[124] <- "007-1D1"

div.ind <- match(diversity$group[diversity$method=="ave"], metadata$sample)
div.group <- metadata$group[div.ind]
div.time <- metadata$time[div.ind]
div.abx <- metadata$abx[div.ind]
div.day <- metadata$day[div.ind]

delay.invsimp <- diversity$invsimpson[div.time=="delayed" & diversity$method=="ave"]
delay.shannon <- diversity$shannon[div.time=="delayed" & diversity$method=="ave"]
delay.abx <- div.abx[div.time=="delayed" & diversity$method=="ave"]
delay.day <- div.day[div.time=="delayed" & diversity$method=="ave"]
delay.group <- div.group[div.time=="delayed" & diversity$method=="ave"]

delay.diversity <- cbind(group=delay.group, day=delay.day, abx=delay.abx, invsimp=delay.invsimp, shannon=delay.shannon)

recov.diversity <- matrix(nrow=7)
row.names(recov.diversity) <- c(-11, -5:0)

amp.div <- matrix(nrow=7, ncol=2)
row.names(amp.div) <- c(-11, -5:0)
colnames(amp.div) <- c("amp.avg", "amp.se")
library(plotrix)
for(j in 1:7){
  matches <- delay.diversity[,3]=="amp" & delay.diversity[,2]==row.names(amp.div)[j]
  amp.div[j, "amp.avg"] <- mean(as.numeric(delay.diversity[matches, "invsimp"]))
  amp.div[j, "amp.se"] <- std.error(as.numeric(delay.diversity[matches, "invsimp"]))
}

metro.div <- matrix(nrow=7, ncol=2)
row.names(metro.div) <- c(-11, -5:0)
colnames(metro.div) <- c("metro.avg", "metro.se")
for(j in 1:7){
  matches <- delay.diversity[,3]=="metro" & delay.diversity[,2]==row.names(metro.div)[j]
  metro.div[j, "metro.avg"] <- mean(as.numeric(delay.diversity[matches, "invsimp"]))
  metro.div[j, "metro.se"] <- std.error(as.numeric(delay.diversity[matches, "invsimp"]))
}

recov.diversity <- cbind(amp.div, metro.div)

# Plot for second part of supplemental figure 2
transpose <-t(recov.diversity)
colors <- c(amp="#6600FF",
            metro="#FF00DBFF")
par(mar=c(5, 5, 0.5, 0.5), las = 2, mgp=c(3, 1, 0))
bp <- barplot(transpose[c("amp.avg", "metro.avg"), ], beside=T, ylim=c(0, 15), 
              ylab="Inverse Simpson Diversity", xlab="", 
              col=colors, xaxt='n' )
xticks <- apply(bp, 2, mean)
axis(1, at=xticks, label=c(-11, -5:0), las=1)
mtext(text = expression(paste("Days Pre-", italic("C. difficile"), " Challenge")), side = 1, line = 3, cex = 1.5, las=0)
abline(v=mean(xticks[1:2]), lty="dashed", lwd=3)
box()

x <- c(bp[1,], bp[2,])
y <- as.numeric(c(transpose[1,], transpose[3,]))
se <- as.numeric(c(transpose[2,], transpose[4,]))
d <- as.data.frame( cbind(x=x, y=y, se=se  ) )

library(Hmisc)
with (
  data = d
  , expr = errbar(x, y, y+se, y-se, add=T, pch=".", cap=.01)
)

legend("topright",inset=0.08, legend=c("Ampicillin", "Metronidazole"), 
       col=colors, pch=15, bty="n", y.intersp=1.5, pt.cex = 2.5, cex=1.2)

> ### Statistical comparison of delayed and on time CFU results
